---
title: "Introduction to Statistical Learning - Ch4 - Ex10"
author: "Thalles Quinaglia Liduares"
date: "23/03/2023"
output: html_document
---

This question should be answered using the Weekly data set, which
is part of the ISLR package. This data is similar in nature to the
Smarket data from this chapter’s lab, except that it contains 1, 089
weekly returns for 21 years, from the beginning of 1990 to the end of
2010.

(a) Produce some numerical and graphical summaries of the Weekly
data. Do there appear to be any patterns? 
Upload packages 

```{r, message=FALSE}
library(ISLR)
library(MASS)
library(caret)
```

Upload data

```{r}
data<-ISLR::Weekly
```

View structure of Weekly data

```{r}
str(Weekly)
```

summary statistics

```{r}
summary(Weekly)
```

(b) Use the full data set to perform a logistic regression with
Direction as the response and the five lag variables plus Volume
as predictors. Use the summary function to print the results. Do
any of the predictors appear to be statistically significant? If so,
which ones?


Fit a logistic regression model

```{r}
 
model <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, family = binomial)

```
Print the summary of the model

```{r}
summary(model)
```

Based on the p-values in the summary output, we can see that only the intercept and the Lag1 variable have a statistically significant relationship with the response variable Direction at a significance level of 0.05. The p-values for the other predictor variables are all greater than 0.05, indicating that they are not statistically significant predictors in this model.

Therefore, we can conclude that only the intercept and the Lag1 variable are statistically significant predictors of the Direction variable in this logistic regression model.

(c) Compute the confusion matrix and overall fraction of correct
predictions. Explain what the confusion matrix is telling you
about the types of mistakes made by logistic regression.


```{r}
# Make predictions using the logistic regression model
predictions <- ifelse(predict(model, Weekly, type = "response") > 0.5, "Up", "Down")

# Create a confusion matrix
conf_mat <- table(predictions, Weekly$Direction)

# Print the confusion matrix
conf_mat

# Calculate the overall fraction of correct predictions
correct_frac <- mean(predictions == Weekly$Direction)
correct_frac
```
The overall fraction of correct predictions for this model is 56.04%, which means that the model correctly predicted the direction of the stock market for slightly more than half of the weeks in the data set.


(d) Now fit the logistic regression model using a training data period
from 1990 to 2008, with Lag2 as the only predictor. Compute the
confusion matrix and the overall fraction of correct predictions
for the held out data (that is, the data from 2009 and 2010).

```{r}
# Create a training data set from 1990 to 2008, with Lag2 as the only predictor
train <- subset(Weekly, Year < 2009, select=c("Direction", "Lag2"))

# Create a testing data set from 2009 to 2010, with Lag2 as the only predictor
test <- subset(Weekly, Year >= 2009, select=c("Direction", "Lag2"))

# Fit a logistic regression model to the training data set
model <- glm(Direction ~ Lag2, data = train, family = binomial)

# Make predictions on the testing data set
probabilities <- predict(model, newdata = test, type = "response")
predictions <- ifelse(probabilities > 0.5, "Up", "Down")

# Compute the confusion matrix and the overall fraction of correct predictions
table(predictions, test$Direction)
accuracy <- mean(predictions == test$Direction)
accuracy
```

The accuracy of the model is equal to 62.5%.

(e) Repeat (d) using LDA (Linear discriminant analysis)

Fit the LDA model on the training data

```{r}
lda_model <- lda(Direction ~ Lag2, data = train)
```

Make predictions on the held out data using the fitted LDA model
```{r}

lda_pred <- predict(lda_model, newdata = test)
```

confusion matrix

```{r}
confusionMatrix(lda_pred$class, test$Direction)$table
confusionMatrix(lda_pred$class, test$Direction)$overall["Accuracy"]
```

