---
title: "An introduction to statistical learning - Ch4 - Ex13"
author: "Thalles Quinaglia Liduares"
date: "23/03/2023"
output: html_document
---

Using the Boston data set from ISLR package, fit classification models in order to predict
whether a given suburb has a crime rate above or below the median.
Explore logistic regression, LDA, and KNN models using various subsets of the predictors. 

Upload package


```{r, message=FALSE}
library(ISLR2)
```

Upload data 

```{r}
Boston<-ISLR2::Boston
```
Binary variable highcrime indicates whether the crime rate is above or below the median

```{r}
Boston$highcrime <- ifelse(Boston$crim > median(Boston$crim), 1, 0)
table(Boston$highcrime)
```
Logistic regression 

```{r}
fit1 <- glm(highcrime ~ ., data = Boston, family = "binomial")
summary(fit1)
```

We can see that all variables are significant except `age` and `dis`.

LDA model

```{r}
library(MASS)
fit2 <- lda(highcrime ~ zn + indus + nox + rm + tax + ptratio  + lstat, data = Boston)
fit2
```

```{r}
library(class)
x <- subset(Boston, select = c(zn, indus, nox, rm, tax, ptratio, lstat))
y <- Boston$highcrime
set.seed(123)
train <- sample(1:nrow(Boston), nrow(Boston)/2)
test <- setdiff(1:nrow(Boston), train)
yhat <- knn(x[train,], x[test,], y[train], k = 5)
mean(yhat == y[test])
```

We can see that the KNN model has the highest accuracy among the three models (85.2%).

Overall, we found that the KNN model performed the best in predicting whether a given suburb has a crime rate above or below the median, using a subset of significant variables
