---
title: "An introduction to statistical learning - Ch8 - Ex8"
author: "Thalles Quinaglia Liduares"
date: "24/03/2023"
output: html_document
---

In the lab, a classification tree was applied to the Carseats data (islr r package) set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches,
treating the response as a quantitative variable.

(a) Split the data set into a training set and a test set.

Upload packages 

```{r}

library(ISLR)
library(caret)

```

```{r}

# set the seed 

# split the data into a training set (70%) and a test set (30%)

trainIndex <- createDataPartition(Carseats$Sales, p = 0.7, list = FALSE)
training <- Carseats[trainIndex, ]
testing <- Carseats[-trainIndex, ]
```

(b) Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?

```{r}
library(rpart)

# fit a regression tree to the training set

fit <- rpart(Sales ~ ., data = training, method = "anova")

```

```{r}

# plot the tree

plot(fit)

text(fit, use.n = TRUE, all = TRUE, cex = 0.8)
```

```{r}

# predict Sales on the test set

predictions <- predict(fit, testing)
```

```{r}

# calculate the test MSE

mse <- mean((testing$Sales - predictions)^2)

mse
```
(c) Use cross-validation in order to determine the optimal level of
tree complexity. Does pruning the tree improve the test MSE?

```{r}

# fit a regression tree with cross-validation

fit.cv <- rpart(Sales ~ ., data = training, method = "anova",
                control = rpart.control(cp = 0.01),
                parms = list(split = "information"),
                cp = seq(0, 0.1, by = 0.001))
```

```{r}

# plot the cross-validation error

plotcp(fit.cv)

```

```{r}

# prune the tree

prune.fit <- prune(fit.cv, cp = fit.cv$cptable[which.min(fit.cv$cptable[, "xerror"]), "CP"])

```

```{r}
# plot the pruned tree
plot(prune.fit)
text(prune.fit, use.n = TRUE, all = TRUE, cex = 0.8)
```

```{r}
# predict Sales on the test set
predictions <- predict(prune.fit, testing)
```

```{r}

# calculate the test MSE

mse <- mean((testing$Sales - predictions)^2)
mse
```


```{r}
library(randomForest)
```

```{r}
# fit a random forest model to the training set
fit <- randomForest(Sales ~ ., data = training, ntree = 500, mtry = 3)

```

```{r}

# predict Sales on the test set
predictions <- predict(fit, testing)

```

```{r}
# calculate the test MSE
mse <- mean((testing$Sales - predictions)^2)
mse
```



